### 2016-02-22 paper.tex
Add reference model to title
Add comment on how low Re results are consistent with SAFL

{\Large \textbf\newline{Experimental Study of a Medium Solidity Cross-Flow
        Turbine with Tapered Blades}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. The tendency of $C_P$ to continue increasing slightly could be
an effect of flow curvature---caused by the finite $c/R$---which imparts a
``virtual camber'' \cite{Migliore1980}, or can be thought of as producing a
``lead'' in angle of attack since cambered airfoils have non-zero lift at zero
angle of attack \cite{Goude2012}. The weaker $Re$-independence of the RM2
compared to that of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.

>>>>

{\Large \textbf\newline{Experimental Study of a Reference Model Cross-Flow
        Turbine with Tapered Blades}} \newline % Insert author names,
% affiliations
% and corresponding author email (do not
% include
% titles, positions, or degrees).
\\ Peter Bachant\textsuperscript{1,*}, Martin Wosnik\textsuperscript{1,*}, Budi
Gunawan\textsuperscript{2}, Vincent S. Neary\textsuperscript{2} \\ \bigskip
\bf{1} Center for Ocean Renewable Energy, University of New Hampshire, Durham,
NH, 03857, USA \\ \bf{2} Water Power Technologies, Sandia National Laboratories,
P.O. Box 5800, Albuquerque, New Mexico 87185-MS1124, USA \\ \bigskip

@@

The behavior of the power and drag coefficients at $\lambda=3.1$ are plotted in
Fig.~\ref{fig:perf-re-dep}, where we can see a Reynolds number independent value
of $C_D$ was observed. The power coefficient of the turbine increases
dramatically below $Re_D = 1 \times 10^6$ or $Re_c \equiv \lambda U_\infty c /
\nu \approx 2 \times 10^5$, beyond which there appears to be a small, linear,
positive trend. At the lowest Reynolds number, mean power coefficient even drops
below zero, which is consistent with the low performance of the 1:15 scale RM2
physical model study~\cite{Hill2014}.

The tendency of $C_P$ to continue increasing slightly could be
an effect of flow curvature---caused by the finite $c/R$---which imparts a
``virtual camber'' \cite{Migliore1980}, or can be thought of as producing a
``lead'' in angle of attack since cambered airfoils have non-zero lift at zero
angle of attack \cite{Goude2012}. The weaker $Re$-independence of the RM2
compared to that of the higher $c/R$ UNH-RVAT could be due to this virtual
camber effect, since camber has been shown to cause earlier $Re$-convergence of
the CFT's geometric torque coefficient when calculated from static foil
coefficients given by a viscous panel method, whereas characteristics like
lift-to-drag ratio do not converge as strongly \cite{Bachant2016-RVAT-Re-dep}.
